An Improved ANS Transaction Template

### 2018-01-26 paper.tex

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

\subsubsection{Case 1}
The case 1 is design to allow configure 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{tab:cascadelvl}. The different cascades don't have the same
geometry: the number of centrifuges per stage depends on their own design and
varies slightly from a level to another.

>>>>

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

\subsubsection{Case 1}
The case 1 is designed to configure 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), all designed the same way. The basic properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsubsection{Case 2}
Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{tab:cascadelvl}. The different cascades don't have the same
geometry: the number of centrifuges per stage depends on their own design and
varies slightly from a level to another.
%we haven't defined a level
